Figures

### 2016-01-26 scripts/figures.Rmd
page breaks

---
title: "Figures"
author: "JT McCrone"
date: "December 30, 2015"
output: html_document
---

@@

Figure 1. An example ROC. A) Hypothetical variants are stratified by p value. True variants are shown as filled circles, while those corresponding to RT, PCR, or sequencing errors are shown as open circles. Potential thresholds are indicated as colored lines. B) An ROC made from the data shown in A. The colored lines indicate the points made by the thresholds in A.

```{r,roc_helper_runctions}
find_freq<-function(Id){ # helper function to get the expected frequency from the sample name
  if(Id=="Covaris_5"){
    x=0.05} else if ( Id=="Covaris_25"){
    x=0.025} else if ( Id=="Covaris_125"){
    x=0.0125} else if ( Id=="Covaris_063"){
    x=0.0063} else if ( Id=="Covaris_016"){
    x=0.0016}
}

@@

Figure 2. Initial DeepSNY accuracy. A) RT-PCR amplified WSN33 genomes were diluted into PR8 at decreasing frequencies and sequenced on an Illumina Miseq. B) An ROC showing our ability to identify WSN33 SNV relative to PR8 at the indicated frequencies. C) A table of the DeepSNV accuracy at a p value threshold of 0.01.

@@

@@

Figure 5. The accuracy of the common variant caller Lofreq. The variant caller Lofreq was applied to the 10 $^5$ genomes/$\mu$l samples. A) An ROC of the accuracy of Lofreq using standard parameters. The specificity of the caller was scaled to account for the same number of tests as the DeepSNV algorithm. Lofreq provides qualtiy scores instead of p values. These were used to set cutoffs for the ROC. B) A table summarizing the accuracy of the ROC A.

@@

Figure 8. The accucary of DeepSNV at lower input levels when run in duplicate. A subset of the 10 $^4$ genomes/$\mu$l samples were processed in duplicate to control for RT-PCR errors. A) The accuracy of our varant calling method at 10 $^4$ genomes/$\mu$l is greatly enhanced by requiring putative variants to be found in duplicate RT-PCR reactions. B) A table summarizing the ROC in C at a p value threshold of 0.01.

>>>>

---
title: "Figures"
author: "JT McCrone"
date: "January 25, 2015"
output: pdf_document
---

@@

Figure 1. An example ROC. A) Hypothetical variants are stratified by p value. True variants are shown as filled circles, while those corresponding to RT, PCR, or sequencing errors are shown as open circles. Potential thresholds are indicated as colored lines. B) An ROC made from the data shown in A. The colored lines indicate the points made by the thresholds in A. 
\pagebreak
```{r,roc_helper_runctions}
find_freq<-function(Id){ # helper function to get the expected frequency from the sample name
  if(Id=="Covaris_5"){
    x=0.05} else if ( Id=="Covaris_25"){
    x=0.025} else if ( Id=="Covaris_125"){
    x=0.0125} else if ( Id=="Covaris_063"){
    x=0.0063} else if ( Id=="Covaris_016"){
    x=0.0016}
}

@@

Figure 2. Initial DeepSNV accuracy. A) RT-PCR amplified WSN33 genomes were diluted into PR8 at decreasing frequencies and sequenced on an Illumina Miseq. B) An ROC showing our ability to identify WSN33 SNV relative to PR8 at the indicated frequencies. C) A table of the DeepSNV accuracy at a p value threshold of 0.01.
\pagebreak

@@

\pagebreak

@@

Figure 5. The accuracy of the common variant caller Lofreq. The variant caller Lofreq was applied to the 10 $^5$ genomes/$\mu$l samples. A) An ROC of the accuracy of Lofreq using standard parameters. The specificity of the caller was scaled to account for the same number of tests as the DeepSNV algorithm. Lofreq provides quality scores instead of p values. These were used to set cutoffs for the ROC. B) A table summarizing the accuracy of the ROC A.

\pagebreak

@@

Figure 8. The accuracy of DeepSNV at lower input levels when run in duplicate. A subset of the 10 $^4$ genomes/$\mu$l samples were processed in duplicate to control for RT-PCR errors. A) The accuracy of our variant calling method at 10 $^4$ genomes/$\mu$l is greatly enhanced by requiring putative variants to be found in duplicate RT-PCR reactions. B) A table summarizing the ROC in C at a p value threshold of 0.01.
